Response to the defense feedback

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

Considering the example in figure~\ref{fig:align}, it read data from the array \textsf{T} based on the index ($i$). If the value of index ($i$) is associated with secret information, the example is vulnerable to side-channel attacks. Unlike the example in the previous section, the array \textsf{T} is on the heap. Data on the heap are allocated at different addresses each time. Suppose during the first run, \textsf{T} is allocated at the address \texttt{0xff124800} and \textsf{T} is allocated at the address \texttt{0xff124801} at the second run. For the example in Figure~\ref{fig:align}(a), the index that is used to access the array is always $1$, so it should not be a side-channel vulnerability here. However, because base addresses are different (\texttt{0xff124800} and \texttt{0xff124801}), we get two different memory accesses. Under the circumstance, it is a false positive. Without proper alignment, it can cause false negatives, as the example shown in Figure~\ref{fig:align}(b). In the example, different keys lead to different indexes. However, as $T_0 + i_0$ equals to $T_1 + i_0$, \ctool{} can not observe the difference here, which is a false positive.

@@

There are some possible solutions that can assign the value.
\textbf{Run-time Information.} One example here is the concrete memory address during the runtime. Such a value satisfies the uniqueness characteristic. However, as the example shown in Figure~\ref{fig:align}, it does not have the alignment property.
\textbf{Source Code Information.} Alternatively, we can use the information from the source code. Recent work~\cite{sumner2010memory} proposes using the execution point that allocates the memory cell as the index and tracking the pointer arithmetic to track the pointer that points to the memory. However, such a method may miss the alias symbol that points to the same memory cell.

>>>>

Considering the example in figure~\ref{fig:align}, it read data from the array \textsf{T} based on the index ($i$). If the value of index ($i$) is associated with secret information, the example is vulnerable to side-channel attacks. Unlike the example in the previous section, the array \textsf{T} is on the heap. Data on the heap are allocated at different addresses each time. Suppose during the first run, \textsf{T} is allocated at the address \texttt{0xff124800} and \textsf{T} is allocated at the address \texttt{0xff124801} at the second run. For the example in Figure~\ref{fig:align}(a), the index that is used to access the array is always $1$, so it should not be a side-channel vulnerability here. However, base addresses are different (\texttt{0xff124800} and \texttt{0xff124801}) so we get two different memory accesses. Under the circumstance, it is a false positive. Without proper alignment, it can cause false negatives, as the example shown in Figure~\ref{fig:align}(b). In the example, different keys lead to different indexes. However, as $T_0 + i_0$ equals to $T_1 + i_0$, \ctool{} can not observe the difference here, which is a false positive.

@@

There are some possible solutions to assign the value.

\textbf{Run-time Information.} One example here is the concrete memory address during the runtime. Such a value satisfies the uniqueness characteristic. However, as the example shown in Figure~\ref{fig:align}, it does not have the alignment property.

\textbf{Source Code Information.} Alternatively, we can use the information from the source code. Recent work~\cite{sumner2010memory} proposes using the execution point that allocates the memory cell as the index and tracking the pointer arithmetic to track the pointer that points to the memory. However, such a method may miss the alias symbol that points to the same memory cell.
